Figures for 3-D printed oxygen devices

### 2015-03-06 publishing/latex/plos_template.tex
working on dicussin

The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor as shown in Figure \ref{oxygen-char-figure}.
Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{fig2}.

Bioverification of the devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.

@@

More mRNA stuff for megan to expand

>>>>

\subsection*{Oxygen Control}
The 24 well insert device was quantified with a platinum based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Figure \ref{figure1}.
Oxygen control was able to be controlled in each of the 6 wells equally from one gas input demonstrating the distribution network worked effectively.
The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
A different gas condition can be used in each sepereate iteration of the 6-well unit allowing 6 tecnical replicants of up to 4 different gas conditions in one 24 well plate\ref{figure2}.

\subsection*{Bioverifcation}
Bioverification of the devices ablility to control the gas enviroment is demonstrated with hypoxia influenced expression of mRNA in cancer cells\ref{fig3}.
Oxygen levels of 21, 10, 5, and 0\% are applied to each set of 6 wells.

More mRNA stuff for megan to expand \ref{figure3}

@@
